\section{Decision log}
%\begin{table}[H]%
	%\centering
	\begin{longtable}{|p{.20\textwidth}|p{.60\textwidth}|p{.20\textwidth}|}
		\heading{\textbf{Date}} & \heading{\textbf{Action}} & \heading{\textbf{Signed off}}
		\\\hline
		06/01/2015 at 16:00 & Operation case file opened and team briefing arranged for 16:00 room 157 & EBDN\newline LCSS\newline LLVE\newline APST\\\hline
		06/01/2015 at 18:00 & Asking Norman Sherriff an authorization of investigation to the CEO, Legal Director and his signed authority  & EBDN\newline LCSS\newline LLVE\newline APST\\\hline
		07/01/2015 at 09:00 & Asking for material to analyze more stuff to Jenny King: 
		\begin{itemize}
			\item All emails of M. John Little, Mrs. Marian Maid, M. Fred Tuck (from IT department)
			\item Search and seizure of M. John Little and M. Fred Tuck
			\item The HR policy and signed copies of M. John Little, Mrs. Marian Maid, M. Fred Tuck
		\end{itemize}
		Asking permission to talk to M. John Little, Mrs. Marian Maid, Fred Tuck &  EBDN\newline LCSS\newline LLVE\newline APST\\\hline
		08/01/2015 at 14:30 & Asking some information to the investigation response team (how did the evidences IDs where created and cases when there were 2 post-it). & LCSS\newline APST\\\hline
		08/01/2015 at 15:15 & \underline{\textbf{To the investigation team:}}\newline
		We wanted to know the content of the two CD’s named “MM PIX” (MC0/002 and MC0/006). Those content weren’t accessible.\newline
		We also wanted to know if the evidences MC0/004, MC0/005, MC0/006, MC0/007, MC0/008 and AEI/005 belonged to Fred Tuck.\newline
		\underline{\textbf{To Norman Sherriff:}}\newline
		When we investigated the first data searching for the behavior of M. John Little, we saw the mention of two projects:
		\begin{itemize}
			\item Project \textit{Nomad}
			\item Project \textit{Snow King}
		\end{itemize}
		Those two projects where used as threats from Mrs. Marian Maid to M. John Little:
		\enquote{Also remember, I know about Project \enquote{\textit{Snow King}} and \enquote{\textit{Nomad}}. You ought to have remembered that I live with you and know more that you may think before embarrassing me to the entire office.} (Mrs. Marian Maid to M. John Little).\newline
		\enquote{What do you think you're doing, threatening me?}(M. John Little to Mrs. Marian Maid).\newline
		We then found some CD’s with the name \enquote{\textit{NOMAD}} wrote on it (AEI001 and MC0/007).\newline
		Then, we looked on M. John Little, M. Fred Tuck and Mrs. Marian Maid email box about those projects.\newline
		We found that those two projects are being run by M. John Little and M. Fred Tuck. It appears that those projects are about embezzlement.\newline
		When M. Norman Sherriff heard this, he told us the investigation was changing. We are now in an investigation of a criminal case and not a civil investigation.\newline
		This is the matter of embezzlement. At this moment, we have three suspects :
		\begin{itemize}
			\item M. John Little
			\item M. Fred Tuck
			\item Mrs. Marian Maid
		\end{itemize}
		To continue our investigation, we have the authorization to read the mails of those three persons about the projects \enquote{\textit{Nomad}} and \enquote{\textit{Snow King}}. & EBDN\newline LCSS\newline LLVE\newline APST\\\hline
	\caption{Decision log}
	\label{TAB:1}
	\end{longtable}
%\end{table}