\section{Assignment}
\subsection{09/11/2015}
\subsubsection{Things to know}
\begin{itemize}
 \item ...
\end{itemize}
\subsubsection{What's expected}
\begin{itemize}
 \item Investigate the evidence
 \item Maintain a proper decision log
 \item Write a report to the management
\end{itemize}
The report must have an management summary for non-technical persons. Then, there is the investigation in details (every steps we took, why, when, how, etc\ldots), what were the results of each of those steps, etc\ldots
\subsubsection{Pro-tips}
\begin{itemize}
 \item Look at the reports examples and the decisions log.
 \item Distribute the work, improve efficiency
 \item Don't abuse of copy paste
 \item We'll have to talk to some people in the company
\end{itemize}
If you want to be right on your evidences, you have to respect the chain of custody. Here, if you want to check an evidence, you have to fill a evidence paper (ID of the evidence, description, location, released to, by, etc\ldots). You also take pictures of the evidences before taking them. So, you know the state of it before packing it.\\
\subsection{10/11/2015}
\subsubsection{Question to ask}
\begin{itemize}
	\item What is the thing Mrs. Maid has done and regret now?
	\item Who took some photographs of her?
	\item What's the exact date of the Christmas party?
	\item Who are the \enquote{guys in the office}?
	\item How many pictures does JL have?
	\item What kind of \enquote{leverage} JL have? Only pictures? something else? What's on the USB external drive?
	\item What is the HR policy? Are they any breach of it?
	\item Why JL calls her \enquote{M\&M}?
	\item Pictures showed to whom?
	\item What is the exciting stuff? One which drive?
	\item What are those two projects? Threat for JL?
	\item What's the motive of MM? What does she want?
\end{itemize}
The assignment is a disciplinary matter between MM and JL.\\
Company is okay with bringing their own device but those devices are subject to search and seizure, even if they are your own (in the policy).\\
We contact the legal Director to have the authorization to perform a search and seizure on JL and FT stuffs (because they are both involved in the case). When we have it, we go to the IT to know what we are going to find (computer security, etc\ldots).\\
We then get someone from HR to come with us. We go to the building staff to be able to get to their offices.\\
Then, we get someone from the security team if the suspects get violent.\\
To perform the search and seizure, we do it when the suspects are working (so we have all their devices, computers running, unlocked, etc\ldots). Before entering in the open-space, you have to know the exact location of FT an JL. You have to make 2 groups : 
\begin{itemize}
	\item One to freeze JL
	\item One to freeze FT
\end{itemize}
We have to be sure they don't delete anything. Security is here to do this. Then, you start collecting all the evidences.\\
Regarding the interviews, all the 3 of them refuse to talk to us:
\begin{description}
	\item[MM] \enquote{I have already told you everything, just solve my problem}
	\item[JL] \enquote{This is bullshit. I don't want to talk about this}
	\item[FT] \enquote{This is bullshit. I don't want to talk about this}
\end{description}
After the search and seizure, we have a pack of pictures from JL and FT. We also have a system to make some searches in the mails.
\subsubsection{Tips}
\begin{itemize}
	\item There is a difference between civil law and criminal law.
	\item We are in a bank. They are very strict rules the bank need to complains with.
	\item We are doing thing from the criminal standard.
	\item Remember the scope. If the investigation is going into some trouble, call your lawyer.
	\item If we find something out of the scope, we don't mess up with the cases. We make another case to check if this is important or not.
\end{itemize}