\section{Console hacking for profit and fun}
For some Wii U hacking, just check MRACAM.\\
\subsection{Why?}
To have full control of the console. A lot of people want also to have personal programs running or hardware modification or \enquote{because I can}.\\
\subsection{Homebrew}
It's about running (self-written) software like kodi. Or to make some clusters.\\
Some game designers try to so they have to buy the dev tools.\\
\subsection{Nintendo Entertainment System -- 1983}
Very good specifications for its time (chip 6502).\\
You would want to hack your NES if you put an imported cartridges, the game could not work because of timing problems. If you wanted to play unlicensed cartridges or some \enquote{Roll-your-own}.\\
To hack the console, you can duplicate the CIC ship. Or you can cut the wire going to the reset pin of the processor.
\subsection{Sony PlayStation}
Very high end console (still now). Especially on the music end. It gives a very clean CD output.\\
You'd hack it because of the PAL/NTCS problems.\\
When you write a CD, you have the header, then the data, then the lead-out (means this is the end).\\
Sony put in the lead-in area (information about the CD's, not over-writable) some code that only the console could read.
\subsection{Microsoft XBOX}
32-bit console based on standard PC hardware. The first console to had the online play and support for the hard-drive.
\subsection{PlayStation 3}
First on with one BluRay. 8 core CPU.\\
Hack it for the mediacenter, piracy, etc\ldots\\
George Hotz has hacked the console is 3 days after the release of the console.\\
ECDSA is the public/private key cryptography.
\subsection{XBOX One, PlayStation 4}
The both are not broke yet.\\
The have almost the same hardware.\\
They also are running some common software (W8, DirectX, Skype; OpenBSD, \ldots).
\subsection{Final thoughts}
Hackers have unlimited time, money, motivation, skills and tools. It is just a matter of time before your system is being brake.