\section{Investigation results}
\subsection{Disciplinary matter involving John Little and Marian Maid}
\subsubsection{First emails}
At the beginning of the investigation, we had been handed two emails conversation between Mrs. Marian Maid and M. John Little. In those conversations, we can denote some important information:
\begin{itemize}
 \item Mrs. Marian Maid wants to talk to M. John Little about a picture he has potentially showed to M. Fred Tuck.\\ M. John Little doesn't deny on this and add there \enquote{there's way more exciting stuff on the drive}.
 \item We then learn that M. John Little may have a drive with some compromising pictures of Mrs. Marian Maid. Since the company's HR policy allow to bring some personal devices at work, he might have took it to his workplace.
 \item Mrs. Marian Maid tells M. John Little that this kind of personal matters don't belong in such a working place.
 \item Mrs. Marian Maid then threatens M. John Little when saying \enquote{I know about Project "Snow King" and "Nomad". You ought to have remembered that I live with you and know more that you may think before embarrassing me to the entire office}.\\
 With this threat, we learn something valuable about those projects. Why would she use them as leverage against M. John Little if they didn't had something suspicious?
 \item Finally, M. John Little threatens back Mrs. Marian Maid. He also insults her in the email.
\end{itemize}
With all those information, we were able to ask M. Norman Sherriff the authorization to perform a search and seizure at M. John Little and M. Fred Tuck.\\
We also had the permission to access the email database for Mrs. Marian Maid, M. John Little and M. Fred Tuck.

\subsubsection{Search and seizure}
\paragraph{M. John Little's desk}~\\\par
During the search and seizure of M. John Little's desk, we found the following evidences:
\begin{description}
 \item[AEI 001 (loc B)] CD named \enquote{NOMAD} found under the desk of M. John Little (with a post-it \enquote{FP-05 14:45})
 \item[AEI 002 (loc E)] USB key taped behind M. John Little's screen
 \item[AEI 003 (loc G)] Desktop computer (Dell Optiplex GX620)
 \item[MCO/001 (loc J)] USB key hidden in a desktop vacuum cleaner (Henry Hoover)
 \item[AEI 004 (loc K)] Hard disk drive inside a Pelican case inside a drawer (with a post-it \enquote{SB02 7/3/15 13.54})
 \item[MCO/002 (loc L)] CD named \enquote{MM PIX} inside a drawer
 \item[MCO/003 (loc L)] Camera Canon inside a drawer. We don't know if it contains a memory card and if it is empty or not.
\end{description}
With a first look, we can already be concerned about the contains of evidences \textit{AEI 001} and \textit{MCO/003}. Those two evidences may be linked to the strange project (\textit{NOMAD}) and to the pictures of Mrs. Marian Maid (\enquote{\textit{MM PIX}}).

\paragraph{M. Fred Tuck's desk}
During the search and seizure of M. Fred Tuck's desk, we found the following evidences:
\begin{description}
 \item[MC0/004] Laptop Vostro 1540, USB key (MC0/005) plugged in, CD (MC0/006) inside. Shutdown, battery unplugged
 \item[MC0/005] USB key plugged to the laptop
 \item[MC0/006] CD named \enquote{MM PIX} inside the laptop
 \item[MC0/007] CD named \enquote{NOMAD} taped under M. Fred Tuck desk
 \item[MC0/008] Hard disk drive case (SATA to USB) empty
 \item[AEI 005] USB key taped under M. Fred Tuck
\end{description}
With all those evidences, we can correlate with the ones from M. John Little. They both have two CD's named \enquote{NOMAD} and \enquote{MM PIX}. Depending on the content of those CD's, it could prove that M. John Little has been sharing some pictures to M. Fred Tuck.\\
Also, the fact that all those devices were hidden (under a desk, inside a vacuum cleaner, etc\ldots) is suspicious about their contents.

\subsection{Suspicious activities regarding "Project Nomad" and "Project Snow King"}
We changed the investigation orientation when we digged deeper about what Mrs. Marian Maid said in the email provided to us. She has clearly threaten M. John Little with two project's names: "Project Snow King" and "Project Nomad". As explained before, it was this threat which caused Mrs. Jenny King to call us in order to investigate the subject told in the previous section.\\
While processing and analyzing emails from M. John Little, M. Fred Tuck and Mrs. Marian Maid, it has been discovered that the two projects were linked. As it can be found in a mail from M. Fred Tuck and M. John Little:\\
\begin{verbatim}
From: Fred Tuck <fredtuck-natbank@inbox.com>
Received: from fredtuck-natbank@inbox.com by (127.0.0.1:25) via inbox.com
  (127.0.0.1:25) with [InBox.Com SMTP Server] id 1402031231095.WM55 for
  johnlittle-natbank@inbox.com; Mon, 3 Feb 2014 12:31:08 -0800
To: John Little <johnlittle-natbank@inbox.com>
MessageID: <EF2F31F9CFC.00000662fredtuck-natbank@inbox.com>
Date: 2014-02-03 21:31:08
Subject: Project Snow King

We have a go on this. Contract will be signed by tomorrow.

Contacts and supporting contracts are now ready to implement Nomad. 

Desert Walker and Bedouin are up to support.

I'll PM you the password for those books

Fred.
____________________________________________________________
FREE 3D EARTH SCREENSAVER - Watch the Earth right on your desktop!
Check it out at http://www.inbox.com/earth
\end{verbatim}

The subject "Project Snow King" and the mention of "Nomad" in the same mail prove that these two projects are working together. Nomad is most likely a subsection of Project Snow King. Moreover, it has been found suspicious that two nicknames "Desert Walker" and "Bedouin" were mentioned. At this time, we can not explicitly found the identities of these two supports because of the lack of informations regarding them. Adding this, M. Fred Tuck wrote that he has communicate the password of some books, number of them can not be told, but he did not use the standard mail of his company to do so. Instead he "PMed" them to M. John Little by any over communication system.\\
This email was the starting point of the orientation's change of our investigation. With these informations, the team went to M. Norman Sherriff and presented the proof to him on the 10th of October 2015. As the subject of these mails is most likely speaking about embezzlement, our affectation changed. We stopped the work on M. John Little behavior and started a new one under the criminal law on what can be found about these two projects, who were the actors and what were their subjects.

\subsubsection{Project Nomad}
Project Nomad was the first to be analyzed. This decision was made according to the mails dates found concerned on the name of the project. To do so, we filtered all mails which contained the word "Nomad" in their subject or content. Two mails poped up from the other, both including M. John Little and M. Fred Tuck; email 1 \ref{MailNomad1} email 2 \ref{MailNomad2}. Both of this emails were send after the two emails provided to us by Mrs. Jenny King (which included the behavior problem between Mrs. Marian Maid and M. John Little).\\
In email 1 \ref{MailNomad1}, it is clear that M. John Little and M. Fred Tuck are involved in the "Nomad" project and know the subject really well. They don't mention another person in it so it is most likely that they are the two protagonist of "Nomad".\\
In email 2 \ref{MailNomad2}, the subject of the email is "Nomad" and the project is short on time as they need to prepare what its next step is.

\subsubsection{Project Snow King}
Project Snow King emails were found with the acronym "SK", which probably mean "Snow King". In all the emails found, Mrs. Marian Maid, M. Fred Tuck and M. John Little were involved in the discussions. We already shown one of the mail in the first section. It seems that Mrs. Marian Maid doesn't know as much as the two others persons about this project.\\
In the first email \ref{SnowKing1}, it seems that Mrs. Marian Maid is aware of a problem concerning cash book in the bank and inform M. Fred Tuck about it. The answer of M. Fred Tuck seems most likely to not argue about his point of view and his decisions.\\
In the second email \ref{SnowKing2}, which is a forward of the first mail by M. Fred Tuck to M. John Little. M. Fred Tuck's ton seems to change in this mail though. He seems to be worried about what Mrs. Marian Maid said and inform M. John Little about the situation, asking for his point of view. We can not investigate further because we do not have M. John Little answer to this email.\\
In the last email \ref{SnowKing3}, another character seems to be concerned about the project: M. Robert Hood. It seems that M. John Little is asking him to give Mrs. Marian Maid a certain book on a specific contract with "Bentons International". Mr. Robert Hood is approving John's proposal.\\
The last mail \ref{Bentons} which subject is about Bentons International is more interesting. It's an exchange between M. Fred Tuck and M. John Little. The two persons seems to manipulate M. Robert Hood to accept John's proposal in a specific goal which is not clear. They seem to be happy about Robert's decision as their plan was going as they planned.

\subsubsection{Others}
To add another suspicious activities by M. John Little and M. Fred Tuck, we discovered an email concerning money transfer inside the company. This email \ref{Others} shows that they use a common account to send money to M. Robert Hood in order to be sure they couldn't be touch by the update in the management team.

\subsection{Recommendations}
From the evidences and the discovery we made on previous sections, we can provide the following recommendations:
\begin{itemize}
 \item Conduct some interviews of the three protagonists (M. John Little, M. Fred Tuck and Mrs. Marian Maid) about the projects NOMAD and SNOW KING
 \item Conduct an throughout investigation on all the company's accounts to verify if there is some embezzlement or money laundering
 \item Contact the authorities to let them realize a full investigation with the power vested in them. We can already give them all the evidences proving all the suspicions this investigation found
\end{itemize}
