\section{Case outline}
\subsection{Assignment description}

\subsubsection{Initial assignment}
At the beginning, the assignment was about civil law: Mrs. Marian Maid was complaining about the behavior of M. John Little. Indeed, it appears that M. John Little has been shared some private data about Mrs. Marian Maid to his colleagues during work time.\\
Our assignment has to conclude if M. John Little behavior is violating the company policy or not.\\
To do so, we first had access to two emails between Mrs. Marian Maid and M. John Little and Mrs Marian Maid and M. John Little HR files.

\subsubsection{Second assignment}

While doing the investigation on the first assignment, we discovered some strange emails exchange between M. John Little and M. Fred Tuck about some projects which could be concerning some money embezzlement.\\
After talking with M. Norman Sherriff (Legal Director), he conclude that this was a more important matter to investigate: it was going under criminal law.\\
The first assignment was then put on hold to focus only on this one.

\subsection{Time-line and case information}
\begin{description}
 \item[Summer 2013] Mrs. Marian Maid and M. John Little went on vacation together. During those vacations, Mrs. Marian Maid allowed M. John Little to take some pictures of her in some embarrassing positions.
 \item[December 2013 (Christmas party)] During a Christmas party, Mrs. Marian Maid heard M. John Little was going to show some of the pictures taken during previous summer to some colleagues of him (salesmen).
 \item[2014-02-03 -- Between 02:14 and 12:56] Mrs. Marian Maid and M. John Little exchanged some emails concerning the fact that M. John Little had been showing some pictures to M. Fred Tuck. In those emails, the conversation became heated and threat were made from both sides.\\
 Those emails also teach us that M. John Little may have a drive containing more pictures of Mrs. Marian Maid in some embarrassing positions.
 \item[2014-02-27 -- 14:26] Mrs Marian Maid informed M. John Little that she was moving in with her sister. Their personal relationship was over. 
 \item[2014-12-16 -- 09:30] Mrs. Marian Maid contacts her friend Mrs. Olivia Oyle in HR and is extremely upset about a personal matter. They both arrange to meet in the canteen to have a coffee and discuss the issue.
 \item[2014-12-16 -- 10:15] Mrs. Marian Maid and Mrs Olivia Oyle meet in the canteen. It is obvious to Mrs Olivia Oyle that Mrs Marian Maid has been crying and is visibly upset.  Mrs Olivia Oyle, stating that she is concerned for Mrs Marian Maid's well being, talks to her about what has upset Mrs Marian Maid.
 \item[2015-01-06] We, the investigation team, are called into the office of Mrs. Jenny King (HR) to discuss a matter of concern. She explain to us the matter and ask us to perform an investigation over M. John Little behavior.\\
 She hands out to us two emails between Mrs. Marian Maid and M. John Little and Mrs Marian Maid and M. John Little HR files.
 \item[2015-03-07 -- 10:53 to 13:29] After getting the legal authorization, a search and seizure was done at M. John Little and M. Fred Tuck's offices.
\end{description}
