\subsection{Suspicious activities regarding "Project Nomad" and "Project Snow King"}
We changed the investigation orientation when we digged deeper about what Mrs. Marian Maid said in the email provided to us. She has clearly threaten M. John Little with two project's names: "Project Snow King" and "Project Nomad". As explained before, it was this threat which caused Mrs. Jenny King to call us in order to investigate the subject told in the previous section.\\
While processing and analyzing emails from M. John Little, M. Fred Tuck and Mrs. Marian Maid, it has been discovered that the two projects were linked. As it can be found in a mail from M. Fred Tuck and M. John Little:\\
\begin{verbatim}
From: Fred Tuck <fredtuck-natbank@inbox.com>
Received: from fredtuck-natbank@inbox.com by (127.0.0.1:25) via inbox.com
  (127.0.0.1:25) with [InBox.Com SMTP Server] id 1402031231095.WM55 for
  johnlittle-natbank@inbox.com; Mon, 3 Feb 2014 12:31:08 -0800
To: John Little <johnlittle-natbank@inbox.com>
MessageID: <EF2F31F9CFC.00000662fredtuck-natbank@inbox.com>
Date: 2014-02-03 21:31:08
Subject: Project Snow King

We have a go on this. Contract will be signed by tomorrow.

Contacts and supporting contracts are now ready to implement Nomad. 

Desert Walker and Bedouin are up to support.

I'll PM you the password for those books

Fred.
____________________________________________________________
FREE 3D EARTH SCREENSAVER - Watch the Earth right on your desktop!
Check it out at http://www.inbox.com/earth
\end{verbatim}

The subject "Project Snow King" and the mention of "Nomad" in the same mail prove that these two projects are working together. Nomad is most likely a subsection of Project Snow King. Moreover, it has been found suspicious that two nicknames "Desert Walker" and "Bedouin" were mentioned. At this time, we can not explicitly found the identities of these two supports because of the lack of informations regarding them. Adding this, M. Fred Tuck wrote that he has communicate the password of some books, number of them can not be told, but he did not use the standard mail of his company to do so. Instead he "PMed" them to M. John Little by any over communication system.\\
This email was the starting point of the orientation's change of our investigation. With these informations, the team went to M. Norman Sherriff and presented the proof to him on the 10th of October 2015. As the subject of these mails is most likely speaking about embezzlement, our affectation changed. We stopped the work on M. John Little behavior and started a new one under the criminal law on what can be found about these two projects, who were the actors and what were their subjects.

\subsubsection{Project Nomad}
Project Nomad was the first to be analyzed. This decision was made according to the mails dates found concerned on the name of the project. To do so, we filtered all mails which contained the word "Nomad" in their subject or content. Two mails poped up from the other, both including M. John Little and M. Fred Tuck; email 1 \ref{MailNomad1} email 2 \ref{MailNomad2}. Both of this emails were send after the two emails provided to us by Mrs. Jenny King (which included the behavior problem between Mrs. Marian Maid and M. John Little).\\
In email 1 \ref{MailNomad1}, it is clear that M. John Little and M. Fred Tuck are involved in the "Nomad" project and know the subject really well. They don't mention another person in it so it is most likely that they are the two protagonist of "Nomad".\\
In email 2 \ref{MailNomad2}, the subject of the email is "Nomad" and the project is short on time as they need to prepare what its next step is.

\subsubsection{Project Snow King}
Project Snow King emails were found with the acronym "SK", which probably mean "Snow King". In all the emails found, Mrs. Marian Maid, M. Fred Tuck and M. John Little were involved in the discussions. We already shown one of the mail in the first section.