\section{Management summary}
	We've been called by Mrs. Jenny King to investigate a potential bad behavior from M. John Little, who works as a trader in the Bank, and Mrs. Marian Maid, who works as a secretary. It seemed that M. John Little shared with his co-worker, and especially with M. Fred Tuck, some pictures of Mrs. Marian Maid. We knew that the two of them were in a complicated relationship and Mrs. Marian Maid accepted M. John little to take photographs of her in an embarrassing  position. These pictures were the same as those that been shared in the office.\\~\\
From there we investigated by seizing all evidences which can be found at M. John Little and M. Fred Tuck offices, as well as their emails history, to ensure that Mrs. Marian Maid privacy hasn't been compromised in the company. We found some evidences as CDs where "MM pix" (MM was a nickname used by John Little during his relationship with Marian Maid) were written with a red marker on it. One CD was found in each of the man offices which proved that M. John Little leaked some private matter in his office.\\~\\
We continued to investigate as we found some informations about two projects named "Project Snow King" and "Nomad". These two projects were linked in the emails and involved always the same actors: M. John Little and M. Fred Tuck. The team most likely think that the two men are performing some kind of embezzlement from some of the Bank's cash books, for their own profit. It seems that Mrs. Marian Maid was implicated in these projects without her knowing, but we couldn't find any evidence showing she was clearly involved in one or both projects. Nevertheless, in a mail provided to us by Mrs. Jenny King, Marian Maid was most likely aware of the two projects and threatened John Little with them, likely to protect herself from him and is leaked pictures. However she may be guilty of not reporting such matter to her superior or the legal director of the company, M. Norman Sherriff.\\~\\
We told M. Norman Sherriff about the matter, and he expressly order us to suspend the current investigation concerning M. John Little's behavior, and to seek more details about the possible embezzlement performed the two men concerned in the trade floor. As we said, we could not find solids proofs, which could show that they were clearly involved in such crime, with the evidence we had at our disposal. We could only identify emails containing the two projects names, showing that M. John Little and M. Fred Tuck's behavior were quite suspicious when they were dealing with these projects.